Titeln på avhandlingens språk

### 2022-08-22 publications/2019EdgeDroid/paper_body.tex
working

\begin{figure}[b]
    \centering
    \input{img/pipeline.tex}
    \caption{Pipeline of human-in-the-loop applications.}\label{fig:pipeline2}
\end{figure}

@@

\begin{figure}[tb]
    \centering
    \input{img/taskmodel.tex}
    \captionof{figure}{Segment of the internal task model of a linear task-guidance WCA.}%
    \label{fig:taskmodel}
\end{figure}

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=.7\columnwidth]{img/TraceReplay_GenArch}
    \caption{Architecture of the benchmarking suite.}\label{fig:TraceReplayArch}
\end{figure}

@@

\begin{figure}[tb]
    \centering
    \input{img/usermodel.tex}
    \captionof{figure}{Preliminary user model.}\label{fig:usermodel}
\end{figure}

@@

\begin{figure}
    \centering%
    \includegraphics[width=.85\columnwidth]{plots/comparison/nofonts/rtt_fb_vs_nofb}%
    \caption{Comparison of round-trip-times for inputs that triggered a state transition in the task model versus inputs that did not.}%
    \label{fig:comparison:rtt}%
\end{figure}%
\begin{figure}
    \centering%
    \includegraphics[width=.85\columnwidth]{plots/comparison/nofonts/box_feedback}%
    \caption{Distribution of latency across system components for inputs that triggered a state transition in the task model.}%
    \label{fig:comparison:feedback}%
\end{figure}%
\begin{figure}%
    \centering%
    \includegraphics[width=.85\columnwidth]{plots/comparison/nofonts/box_taskstep}%
    \caption{Round-trip-times for input-feedback cycles associated with state transitions in the internal task model for a single client connected over an optimal wireless link.}%
    \label{fig:comparison:tasksteps}
\end{figure}%

>>>>

\begin{figure}[b]
    \centering
    \input{publications/2019EdgeDroid/img/pipeline.tex}
    \caption{Pipeline of human-in-the-loop applications.}\label{fig:pipeline2}
\end{figure}

@@

\begin{figure}[tb]
    \centering
    \input{publications/2019EdgeDroid/img/taskmodel.tex}
    \captionof{figure}{Segment of the internal task model of a linear task-guidance WCA.}%
    \label{fig:taskmodel}
\end{figure}

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=.7\columnwidth]{publications/2019EdgeDroid/img/TraceReplay_GenArch}
    \caption{Architecture of the benchmarking suite.}\label{fig:TraceReplayArch}
\end{figure}

@@

\begin{figure}[tb]
    \centering
    \input{publications/2019EdgeDroid/img/usermodel.tex}
    \captionof{figure}{Preliminary user model.}\label{fig:usermodel}
\end{figure}

@@

\begin{figure}
    \centering%
    \includegraphics[width=.85\columnwidth]{publications/2019EdgeDroid/plots/comparison/nofonts/rtt_fb_vs_nofb}%
    \caption{Comparison of round-trip-times for inputs that triggered a state transition in the task model versus inputs that did not.}%
    \label{fig:comparison:rtt}%
\end{figure}%
\begin{figure}
    \centering%
    \includegraphics[width=.85\columnwidth]{publications/2019EdgeDroid/plots/comparison/nofonts/box_feedback}%
    \caption{Distribution of latency across system components for inputs that triggered a state transition in the task model.}%
    \label{fig:comparison:feedback}%
\end{figure}%
\begin{figure}%
    \centering%
    \includegraphics[width=.85\columnwidth]{publications/2019EdgeDroid/plots/comparison/nofonts/box_taskstep}%
    \caption{Round-trip-times for input-feedback cycles associated with state transitions in the internal task model for a single client connected over an optimal wireless link.}%
    \label{fig:comparison:tasksteps}
\end{figure}%
